---
title: "Comparison of all ChIP Targets"
author: "Stephen Pederson"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(message = FALSE, wraning = FALSE)
```


## Introduction

```{r pkg}
library(tidyverse)
library(magrittr)
library(extraChIPs)
library(plyranges)
library(pander)
library(scales)
library(reactable)
library(htmltools)
library(UpSetR)
library(rtracklayer)
library(GenomicInteractions)
library(multcomp)
library(glue)
theme_set(theme_bw())
```


```{r dht-peaks}
dht_peaks <- here::here("data", "peaks") %>% 
  list.files(recursive = TRUE, pattern = "oracle", full.names = TRUE) %>% 
  sapply(read_rds, simplify = FALSE) %>% 
  lapply(function(x) x[["DHT"]]) %>% 
  lapply(setNames, nm = c()) %>% 
  setNames(str_extract_all(names(.), "AR|FOXA1|GATA3|TFAP2B"))
dht_consensus <- dht_peaks %>%
  lapply(granges) %>% 
  GRangesList() %>% 
  unlist() %>% 
  reduce() %>% 
  mutate(
    AR = overlapsAny(., dht_peaks$AR),
    FOXA1 = overlapsAny(., dht_peaks$FOXA1),
    GATA3 = overlapsAny(., dht_peaks$GATA3),
    TFAP2B = overlapsAny(., dht_peaks$TFAP2B),
  )
targets <- names(dht_peaks)
sq <- seqinfo(dht_consensus)
```

## Relationship Between Binding Regions

Oracle peaks from the DHT-treated samples in each ChIP target were obtained previously using the GRAVI workflow.
AR and GATA3 peaks were derived from the same samples/passages, whilst FOXA1 and TFAP2B ChIP-Seq experiments were performed separately.

```{r tbl-overlap}
cp <- htmltools::tags$em(
  "Summary of all oracle peaks from DHT-treated samples. FOXA1 clearly showed the most binding activity."
)
tbl <- dht_peaks %>% 
  lapply(
    function(x) {
      tibble(
        n = length(x),
        w = median(width(x)),
        kb = sum(width(x)) / 1e3
      )
    }
  ) %>% 
  lapply(list) %>% 
  as_tibble() %>% 
  pivot_longer(cols = everything(), names_to = "target") %>% 
  unnest(everything()) %>% 
  reactable(
    filterable = FALSE, searchable = FALSE,
    columns = list(
      target = colDef(name = "ChIP Target"),
      n = colDef(name = "Total Peaks"),
      w = colDef(name = "Median Width"),
      kb = colDef(name = "Total Width (kb)", format = colFormat(digits = 1))
    ),
    defaultColDef = colDef(
      format = colFormat(separators = TRUE, digits = 0)
    )
  )
div(class = "table",
  div(class = "table-header",
      div(class = "caption", cp),
      tbl
  )
)
```

A set of target-agnostic set of binding regions was then defined as the union of all DHT-treat peaks across all targets.

```{r upset-dht-consensus, fig.cap = "Using the union of all binding regions, those which overlapped an oracle peak from each ChIP target are shown"}
dht_consensus %>% 
  as_tibble() %>% 
  pivot_longer(cols = all_of(targets), names_to = "target", values_to = "bound") %>% 
  dplyr::filter(bound) %>% 
  split(.$target) %>% 
  lapply(pull, "range") %>% 
  fromList() %>% 
  upset(
    sets = rev(targets), keep.order = TRUE, 
    order.by = "freq", 
    set_size.show = TRUE, set_size.scale_max = nrow(.)
  )
```

## H3K27ac Signal

Given the hypothesis that the co-ocurrence of all 4 ChIP targets should be associated with increased transcriptional or regulatory activity, the set of all DHT peaks were then compared to promoters and enahncers derived H2K27ac binding, as detected in the existing GATA3/AR dataset produced by Leil Hosseinzadeh.
Any H3K27ac peak detected in this dataset was classified either as a promoter or enhancer, and thus these features can be considered as the complete set of regions with detectable H3K27ac signal from this experiment.

```{r features}
all_gr <- here::here("data", "annotations", "all_gr.rds") %>% 
  read_rds() 
tss <- resize(all_gr$transcript, width = 1)
features <- here::here("data", "h3k27ac") %>% 
  list.files(full.names = TRUE, pattern = "bed$") %>% 
  sapply(import.bed, seqinfo = sq) %>% 
  lapply(granges) %>% 
  setNames(basename(names(.))) %>% 
  setNames(str_remove_all(names(.), "s.bed")) %>% 
  GRangesList() %>% 
  unlist() %>% 
  names_to_column("feature") %>% 
  sort()
dht_consensus$H3K27ac <- overlapsAny(dht_consensus, features)
dht_consensus$dist_to_tss <- dht_consensus %>% 
  distanceToNearest(tss, ignore.strand = TRUE) %>% 
  mcols() %>% 
  .[["distance"]]
```


```{r}
cp <- htmltools::tags$em(
  glue(
    "Summary of all sites, taking the union of all sites with any target bound. ",
    "{comma(length(dht_consensus))} sites were found across all targets. ",
    "Individual ChIP targets can be searched within this table using 't' or 'f' ",
    "to denote True or False. Summaries regarding association with H3K27ac ", 
    "peaks and distance to the nearest TSS are also provided."
  )
)
tbl <- dht_consensus %>% 
  as_tibble() %>% 
  group_by(!!!syms(targets)) %>% 
  summarise(
    n = dplyr::n(),
    H3K27ac = mean(H3K27ac),
    d = median(dist_to_tss),
    .groups = "drop"
  ) %>% 
  arrange(desc(n)) %>% 
  reactable(
    filterable = TRUE,
    columns = list(
      AR = colDef(
        cell = function(value) {
          ifelse(value, "\u2714", "\u2716")
        }, 
        style = function(value) {
          cl <- ifelse(value, "forestgreen", "red")
          list(color = cl)
        }
      ),
      FOXA1 = colDef(
        cell = function(value) {
          ifelse(value, "\u2714", "\u2716")
        }, 
        style = function(value) {
          cl <- ifelse(value, "forestgreen", "red")
          list(color = cl)
        }
      ),
      GATA3 = colDef(
        cell = function(value) {
          ifelse(value, "\u2714", "\u2716")
        }, 
        style = function(value) {
          cl <- ifelse(value, "forestgreen", "red")
          list(color = cl)
        }
      ),
      TFAP2B = colDef(
        cell = function(value) {
          ifelse(value, "\u2714", "\u2716")
        }, 
        style = function(value) {
          cl <- ifelse(value, "forestgreen", "red")
          list(color = cl)
        }
      ),
      n = colDef(
        name = "Nbr. Sites",
        format = colFormat(separators = TRUE)
      ),
      H3K27ac = colDef(
        name = "% Overlapping H3K27ac Peak",
        format = colFormat(percent = TRUE, digits = 2)
      ),
      d = colDef(
        name = "Median Distance to Nearest TSS (bp)",
        format = colFormat(digits = 0, separators = TRUE)
      )
    )
  )
div(class = "table",
  div(class = "table-header",
      div(class = "caption", cp),
      tbl
  )
)
```


```{r glm-h3k27ac}
grp_h3k27ac <- dht_consensus %>% 
  as_tibble() %>% 
  dplyr::select(range, all_of(targets), H3K27ac) %>% 
  pivot_longer(cols = all_of(targets), names_to = "targets") %>% 
  dplyr::filter(value) %>% 
  group_by(range, H3K27ac) %>% 
  summarise(targets = paste(targets, collapse = "+"), .groups = "drop")
glm_h3k27ac <- glm(H3K27ac ~ 0 + targets, family = "binomial", data = grp_h3k27ac)
```

A simple logistic regression model was then run to estimate the probability of overlapping a peak associated with the histone mark H3K27ac for each combination of ChIP targets.
Binding of TFAP2$\beta$ in isolation clearly had the strongest association with H3K27ac peaks, whilst the absence of TFAP2$\beta$ clearly reduced the likelihood of all other ChIP targets being associated with H3K27ac signal.


```{r confint-glm-h3k27ac, fig.cap = "Family-wise 95% Confidence Intervals for the probability of overlapping an H3K27ac-derived feature, based on the combinations of detected ChIP targets."}
inv.logit <- binomial()$linkinv
glm_h3k27ac %>% 
  glht() %>% 
  confint() %>% 
  .[["confint"]] %>% 
  as_tibble(rownames = "targets") %>% 
  mutate(
    n_targets = str_count(targets, "\\+") + 1
  ) %>% 
  arrange(desc(n_targets), desc(targets)) %>% 
  mutate(
    targets = fct_inorder(targets) %>% 
      fct_relabel(str_remove_all, pattern = "targets"),
    p = inv.logit(Estimate),
    TFAP2B = ifelse(str_detect(targets, "TFAP2B"), "TFAP2B", "No TFAP2B"),
    across(all_of(c("upr", "lwr")), inv.logit)
  ) %>% 
  ggplot(aes(p, targets)) + 
  geom_point() +
  geom_errorbarh(aes(xmin = lwr, xmax = upr), height = 0.4, colour = "grey20") +
  facet_grid(TFAP2B ~ ., scales = "free_y") +
  labs(x = "Probability of H3K27ac Peak Overlap", y = "Detected Targets")
```

### Distance to Nearest TSS

The distance to the nearest TSS was also checked for each of the union peaks, with the vast majority of TFAP2$\beta$-only peaks being with 1kb of a TSS, indicating a fundamental role for TFAP2$\beta$ in transcriptional regulation.
These were much further away when bound in combination with other ChIP targets, to the point that most sites where all four were found bound were >3kb from any TSS, suggesting that an alternative role for TFAP2$\beta$ is enhancer-based gene regulation, when acting in concert with the remaining targets.

```{r dist-to-tss, fig.cap = "Distance to the nearest TSS for all peaks detected with one or more of the required ChIP targets."}
dht_consensus %>% 
  as_tibble() %>% 
  dplyr::select(range, all_of(targets), dist_to_tss, H3K27ac) %>% 
  pivot_longer(cols = all_of(targets), names_to = "targets") %>% 
  dplyr::filter(value) %>% 
  group_by(range, dist_to_tss, H3K27ac) %>% 
  arrange(range, targets) %>% 
  summarise(targets = paste(targets, collapse = "+"), .groups = "drop") %>% 
  mutate(
    n_targets = str_count(targets, "\\+") + 1,
    TFAP2B = ifelse(str_detect(targets, "TFAP2B"), "TFAP2B", "No TFAP2B")
  ) %>% 
  arrange(desc(n_targets), desc(targets)) %>% 
  mutate(targets = fct_inorder(targets)) %>% 
  ggplot(aes(dist_to_tss + 1, targets, fill = H3K27ac)) +
  geom_boxplot() +
  facet_grid(TFAP2B ~ ., scales = "free_y") +
  # coord_cartesian(xlim = c(0, 5e4)) +
  scale_x_log10(labels = comma, breaks = 10^seq(0, 5)) +
  scale_fill_manual(values = c("grey70", rgb(0.9, 0.1, 0.2))) +
  labs(x = "Distance to Nearest TSS (bp+1)", y = "ChIP Targets")
```



### Comparison With H3K27ac HiChIP Data

To perform this step, externally-sourced data defining promoters & enhancers (H3K27ac ChIP-Seq), and H3K27ac-HiChIP obtained from [SRA](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE157381) and [analysed previously](https://github.com/DRMCRL/MDA-MB-453-H3K27Ac-HiChIP), were included.
The H3K27ac-derived features were obtained from the same passages/experiments as GATA3 and AR.
Conversely, the HiChIP data was obtained from a public dataset, not produced with the DRMCRL.
HiChIP interactions were obtained using only the Vehicle controls from an Abemaciclib Vs. Vehicle experiment.



```{r hic}
fl <- here::here("data", "hichip") %>% 
  list.files(full.names = TRUE, pattern = "gi.+rds") 
hic <- GInteractions()
for (f in fl) {
  hic <- c(hic, read_rds(f))
}
hic <- sort(hic)
```

Before proceeding, the comparability of the H3K27ac-HiChIP and H3K27ac-derived features was checked.
`r percent(length(subsetByOverlaps(hic, features)) / length(hic))` of HiChIP long-range interactions overlapped a promoter or enhancer derived from H3K27ac ChIP-seq.
Conversely, `r percent(length(subsetByOverlaps(features, hic)) / length(features))` or ChIP-Seq features mapped to a long-range interaction.

## Mapping To Genes


```{r all-gr}
rnaseq <- here::here("data", "rnaseq", "dge.rds") %>% 
  read_rds()
counts <- here::here("data", "rnaseq", "counts.out.gz") %>% 
  read_tsv(skip = 1) %>% 
  dplyr::select(Geneid, ends_with("bam")) 
detected <- counts %>%
  pivot_longer(
    cols = ends_with("bam"), names_to = "sample", values_to = "counts"
  ) %>% 
  mutate(detected = counts > 0) %>% 
  group_by(Geneid) %>% 
  summarise(detected = mean(detected) > 0.25, .groups = "drop") %>%
  dplyr::filter(detected) %>% 
  pull("Geneid")
```

In order to more accurately assign genes to actively transcribed genes, the RNA-Seq dataset generated in 2013 studying DHT Vs. Vehicle in MDA-MB-453 cells was used.
All `r comma(length(detected))` genes with >1 read in at least 1/4 of the samples was considered to be detected, and peaks were only mapped to detected genes.

```{r map-to-genes}
dht_consensus <- mapByFeature(
  dht_consensus, 
  genes = subset(all_gr$gene, gene_id %in% detected),
  prom = subset(features, feature == "promoter"),
  enh = subset(features, feature == "enhancer"),
  gi = hic
)
all_targets <- dht_consensus %>% 
  as_tibble() %>% 
  dplyr::filter(if_all(targets)) %>% 
  unnest(everything()) %>% 
  distinct(gene_id) %>% 
  pull("gene_id")
```

`r dht_consensus %>% as_tibble() %>% unnest(everything()) %>% distinct(gene_id) %>% nrow() %>%  divide_by(length(detected)) %>% percent()` of detected genes had one or more peaks mapped to them.

Looking specifically at the peaks for which all four targets directly overlapped, `r comma(length(all_targets))` of the `r comma(length(detected))` detected genes were mapped to at least one directly overlapping binding region.

## Apocrine Enrichment

```{r}
hgnc <- read_csv(
  here::here("data", "external", "hgnc-symbol-check.csv"), skip = 1
) %>% 
  dplyr::select(Gene = Input, gene_name = `Approved symbol`)
apo_ranks <- here::here("data", "external", "ApoGenes.txt") %>% 
  read_tsv() %>% 
  left_join(hgnc) %>% 
  left_join(
    as_tibble(all_gr$gene) %>% 
      dplyr::select(gene_id, gene_name),
    by = "gene_name"
  ) %>% 
  dplyr::select(starts_with("gene_"), ends_with("rank")) %>% 
  dplyr::filter(!is.na(gene_id))
```

The Apocrine genes and ranks from [Farmer *et al*](https://www.nature.com/articles/1208561#Sec10) were loaded, updating gene names using the latest release from [HGNC](https://www.genenames.org/tools/multi-symbol-checker/).
`r comma(nrow(apo_ranks))` of the original genes were able to be mapped to gene identifiers matching Gencode release 33.

### Apocrine Ranks

- Need to cut by H3K27Ac
- Check UpSet plot by promoter/enhancer/detected genes

For the purposes of simple exploration, the provided list was sorted by `apo_rank` and the proportion of genes mapped to at least one set of overlapping peaks was compared to these ranks.

```{r}
apo_ranks %>%
  arrange(apo_rank) %>% 
  mutate(
    all = gene_id %in% all_targets,
    n = cumsum(all), 
    p = n / apo_rank
  ) %>% 
  ggplot(aes(apo_rank, p)) + 
  geom_line() + 
  coord_cartesian(xlim= c(0, 1000), ylim = c(0.6, 1))
```

### AB Ranks

The same approach was applied to AB ranks


```{r}
apo_ranks %>%
  dplyr::filter(!is.na(ABrank)) %>% 
  arrange(ABrank) %>% 
  mutate(
    ABrank = seq_along(ABrank),
    all = gene_id %in% all_targets,
    n = cumsum(all), 
    p = n / ABrank
  ) %>% 
  ggplot(aes(ABrank, p)) + 
  geom_line() 
```


### AL Ranks

The same approach was applied to AL ranks


```{r}
apo_ranks %>%
  dplyr::filter(!is.na(ALrank)) %>% 
  arrange(ALrank) %>% 
  mutate(
    ALrank = seq_along(ALrank),
    all = gene_id %in% all_targets,
    n = cumsum(all), 
    p = n / ALrank
  ) %>% 
  ggplot(aes(ALrank, p)) + 
  geom_line() 
```
