---
title: "Comparison of all ChIP Targets"
author: "Stephen Pederson"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, warning = FALSE,
  fig.width = 10, fig.height = 8, dev = c("png", "pdf")
)
```


## Introduction

```{r pkg}
library(tidyverse)
library(magrittr)
library(extraChIPs)
library(plyranges)
library(pander)
library(scales)
library(reactable)
library(htmltools)
library(UpSetR)
library(rtracklayer)
library(GenomicInteractions)
library(multcomp)
library(glue)
library(nnet)
library(effects)
library(Gviz)
library(readxl)
library(corrplot)
library(goseq)
library(BSgenome.Hsapiens.UCSC.hg19)
theme_set(theme_bw())
```

```{r reactable-widgets}
bar_chart <- function(label, width = "100%", height = "16px", fill = "#00bfc4", background = NULL) {
  bar <- div(style = list(background = fill, width = width, height = height))
  chart <- div(style = list(flexGrow = 1, marginLeft = "8px", background = background), bar)
  div(style = list(display = "flex", alignItems = "center"), label, chart)
}
bar_style <- function(width = 1, fill = "#e6e6e6", height = "75%", align = c("left", "right"), color = NULL) {
  align <- match.arg(align)
  if (align == "left") {
    position <- paste0(width * 100, "%")
    image <- sprintf("linear-gradient(90deg, %1$s %2$s, transparent %2$s)", fill, position)
  } else {
    position <- paste0(100 - width * 100, "%")
    image <- sprintf("linear-gradient(90deg, transparent %1$s, %2$s %1$s)", position, fill)
  }
  list(
    backgroundImage = image,
    backgroundSize = paste("100%", height),
    backgroundRepeat = "no-repeat",
    backgroundPosition = "center",
    color = color
  )
}
```



```{r dht-peaks}
dht_peaks <- here::here("data", "peaks") %>% 
  list.files(recursive = TRUE, pattern = "oracle", full.names = TRUE) %>% 
  sapply(read_rds, simplify = FALSE) %>% 
  lapply(function(x) x[["DHT"]]) %>% 
  lapply(setNames, nm = c()) %>% 
  setNames(str_extract_all(names(.), "AR|FOXA1|GATA3|TFAP2B"))
dht_consensus <- dht_peaks %>%
  lapply(granges) %>% 
  GRangesList() %>% 
  unlist() %>% 
  reduce() %>% 
  mutate(
    AR = overlapsAny(., dht_peaks$AR),
    FOXA1 = overlapsAny(., dht_peaks$FOXA1),
    GATA3 = overlapsAny(., dht_peaks$GATA3),
    TFAP2B = overlapsAny(., dht_peaks$TFAP2B),
  )
targets <- names(dht_peaks)
sq <- seqinfo(dht_consensus)
```

## Relationship Between Binding Regions

Oracle peaks from the DHT-treated samples in each ChIP target were obtained previously using the GRAVI workflow.
AR and GATA3 peaks were derived from the same samples/passages, whilst FOXA1 and TFAP2B ChIP-Seq experiments were performed separately.

```{r tbl-overlap}
cp <- htmltools::tags$em(
  "Summary of all oracle peaks from DHT-treated samples. FOXA1 clearly showed the most binding activity."
)
tbl <- dht_peaks %>% 
  lapply(
    function(x) {
      tibble(
        n = length(x),
        w = median(width(x)),
        kb = sum(width(x)) / 1e3
      )
    }
  ) %>% 
  lapply(list) %>% 
  as_tibble() %>% 
  pivot_longer(cols = everything(), names_to = "target") %>% 
  unnest(everything()) %>% 
  reactable(
    filterable = FALSE, searchable = FALSE,
    columns = list(
      target = colDef(name = "ChIP Target"),
      n = colDef(name = "Total Peaks"),
      w = colDef(name = "Median Width"),
      kb = colDef(name = "Total Width (kb)", format = colFormat(digits = 1))
    ),
    defaultColDef = colDef(
      format = colFormat(separators = TRUE, digits = 0)
    )
  )
div(class = "table",
  div(class = "table-header",
      div(class = "caption", cp),
      tbl
  )
)
```

A set of target-agnostic set of binding regions was then defined as the union of all DHT-treat peaks across all targets.

```{r upset-dht-consensus, fig.cap = "Using the union of all binding regions, those which overlapped an oracle peak from each ChIP target are shown"}
dht_consensus %>% 
  as_tibble() %>% 
  pivot_longer(cols = all_of(targets), names_to = "target", values_to = "bound") %>% 
  dplyr::filter(bound) %>% 
  split(.$target) %>% 
  lapply(pull, "range") %>% 
  fromList() %>% 
  upset(
    sets = rev(targets), keep.order = TRUE, 
    order.by = "freq", 
    set_size.show = TRUE, set_size.scale_max = nrow(.)
  )
```

## H3K27ac Signal {.tabset}

Given the hypothesis that the co-ocurrence of all 4 ChIP targets should be associated with increased transcriptional or regulatory activity, the set of all DHT peaks were then compared to promoters and enhancers derived H2K27ac binding, as detected in the existing GATA3/AR dataset produced by Leila Hosseinzadeh.
Any H3K27ac peak detected in this dataset was classified either as a promoter or enhancer, and thus these features can be considered as the complete set of regions with detectable H3K27ac signal from this experiment.

```{r features}
all_gr <- here::here("data", "annotations", "all_gr.rds") %>% 
  read_rds() 
tss <- resize(all_gr$transcript, width = 1)
features <- here::here("data", "h3k27ac") %>% 
  list.files(full.names = TRUE, pattern = "bed$") %>% 
  sapply(import.bed, seqinfo = sq) %>% 
  lapply(granges) %>% 
  setNames(basename(names(.))) %>% 
  setNames(str_remove_all(names(.), "s.bed")) %>% 
  GRangesList() %>% 
  unlist() %>% 
  names_to_column("feature") %>% 
  sort()
dht_consensus %<>% 
  mutate(
    promoter = bestOverlap(., features, var = "feature", missing = "None") == "promoter",
    enhancer = bestOverlap(., features, var = "feature", missing = "None") == "enhancer",
    H3K27ac = promoter | enhancer,
    dist_to_tss = mcols(distanceToNearest(., tss, ignore.strand = TRUE))$distance
  )
```


```{r tbl-h3k27ac-summary}
fs <- 12
cp <- htmltools::tags$em(
  glue(
    "Summary of all sites, taking the union of all sites with any target bound. ",
    "{comma(length(dht_consensus))} sites were found across all targets. ",
    "Individual ChIP targets can be searched within this table using 't' or 'f' ",
    "to denote True or False. Summaries regarding association with H3K27ac ", 
    "peaks and distance to the nearest TSS are also provided. ",
    "The total numbers of sites overlapping H3K27ac-defined Promoters and ", 
    "Enhancers are shown with the % of sites being relative to to those ", 
    "overlapping H3K27ac-defined features"
  )
)
tbl <- dht_consensus %>%
  as_tibble() %>% 
  group_by(!!!syms(targets)) %>% 
  summarise(
    n = dplyr::n(),
    nH3K27ac = sum(H3K27ac),
    H3K27ac = mean(H3K27ac),
    promoter = sum(promoter),
    enhancer = sum(enhancer),
    d = median(dist_to_tss),
    .groups = "drop"
  ) %>% 
  arrange(desc(n)) %T>%
  write_tsv(
    here::here("output/sites_by_h3k27ac.tsv")
  ) %>% 
  reactable(
    filterable = TRUE,
    pagination = FALSE,
    columns = list(
      AR = colDef(
        cell = function(value) {
          ifelse(value, "\u2714", "\u2716")
        }, 
        style = function(value) {
          cl <- ifelse(value, "forestgreen", "red")
          list(color = cl)
        },
        maxWidth = 60
      ),
      FOXA1 = colDef(
        cell = function(value) {
          ifelse(value, "\u2714", "\u2716")
        }, 
        style = function(value) {
          cl <- ifelse(value, "forestgreen", "red")
          list(color = cl)
        },
        maxWidth = 60
      ),
      GATA3 = colDef(
        cell = function(value) {
          ifelse(value, "\u2714", "\u2716")
        }, 
        style = function(value) {
          cl <- ifelse(value, "forestgreen", "red")
          list(color = cl)
        },
        maxWidth = 60
      ),
      TFAP2B = colDef(
        cell = function(value) {
          ifelse(value, "\u2714", "\u2716")
        }, 
        style = function(value) {
          cl <- ifelse(value, "forestgreen", "red")
          list(color = cl)
        },
        maxWidth = 70
      ),
      n = colDef(
        name = "Nbr. Sites",
        format = colFormat(separators = TRUE),
        maxWidth = 75
      ),
      nH3K27ac = colDef(
        name = "Overlapping H3K27ac",
        format = colFormat(separators = TRUE),
        maxWidth = 85
      ),
      H3K27ac = colDef(
        name = "% H3K27ac Overlap",
        format = colFormat(digits = 1, percent = TRUE),
        style = function(value) {
            bar_style(width = value, align = "right")
        },
        maxWidth = 80
      ),
      promoter = colDef(
        name = "Promoters",
        style = function(value, index) {
            bar_style(
              width = 0.5*(value / .$nH3K27ac[[index]]), align = "right", 
              fill = rgb(1, 0.416, 0.416)
            )
        },
        cell = function(value, index) {
          lb <- glue("{value} ({percent(value / .$nH3K27ac[[index]], 1)})")
          as.character(lb)
        },
        align = "left",
        minWidth = 120
      ),
      enhancer = colDef(
        name = "Enhancers",
        style = function(value, index) {
            bar_style(
              width = 0.5*(value / .$nH3K27ac[[index]]), align = "left", 
              fill = rgb(1, 0.65, 0.2)
            )
        },
        cell = function(value, index) {
          lb <- glue("{value} ({percent(value / .$nH3K27ac[[index]], 1)})")
          as.character(lb)
        },
        align = "right",
        minWidth = 120
      ),
      d = colDef(
        name = "Median Distance to TSS (bp)",
        format = colFormat(digits = 0, separators = TRUE)
      )
    ),
    style = list(fontSize = fs)
  )
div(class = "table",
  div(class = "table-header",
      div(class = "caption", cp),
      tbl
  )
)
```

### All H3K27ac Peaks

```{r glm-h3k27ac}
grp_h3k27ac <- dht_consensus %>% 
  as_tibble() %>% 
  dplyr::select(range, all_of(targets), H3K27ac) %>% 
  pivot_longer(cols = all_of(targets), names_to = "targets") %>% 
  dplyr::filter(value) %>% 
  group_by(range, H3K27ac) %>% 
  summarise(targets = paste(targets, collapse = "+"), .groups = "drop")
glm_h3k27ac <- glm(H3K27ac ~ 0 + targets, family = "binomial", data = grp_h3k27ac)
```

A simple logistic regression model was then run to estimate the probability of overlapping a peak associated with the histone mark H3K27ac for each combination of ChIP targets.
Binding of TFAP2$\beta$ in isolation clearly had the strongest association with H3K27ac peaks, whilst the absence of TFAP2$\beta$ clearly reduced the likelihood of all other ChIP targets being associated with H3K27ac signal.


```{r confint-glm-h3k27ac, fig.height=7, fig.cap = "Family-wise 95% Confidence Intervals for the probability of overlapping an H3K27ac-derived feature, based on the combinations of detected ChIP targets."}
inv.logit <- binomial()$linkinv
df <- glm_h3k27ac %>% 
  glht() %>% 
  confint() %>% 
  .[["confint"]] %>% 
  as_tibble(rownames = "targets") %>% 
  mutate(
    n_targets = str_count(targets, "\\+") + 1
  ) %>% 
  arrange(desc(n_targets), desc(targets)) %>% 
  mutate(
    TFAP2B = ifelse(str_detect(targets, "TFAP2B"), "TFAP2B", "No TFAP2B"),
    targets = targets %>% 
      str_remove_all("\\+TFAP2B$") %>% 
      fct_inorder() %>% 
      fct_relabel(str_remove_all, pattern = "targets"),
    p = inv.logit(Estimate),
    across(all_of(c("upr", "lwr")), inv.logit),
    y = case_when(
      str_detect(TFAP2B, "No") ~ as.integer(targets) - 0.2,
      TRUE ~ as.integer(targets) + 0.2
    )
  )
df %>% 
  ggplot(aes(p, y, colour = TFAP2B)) + 
  geom_point() +
  geom_errorbarh(aes(xmin = lwr, xmax = upr), height = 0.4) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(
    breaks = seq_along(levels(df$targets)), labels = levels(df$targets),
    expand = expansion(c(0.02, 0.02))
  ) +
  scale_colour_manual(values = c("black", "red")) +
  labs(x = "Probability of H3K27ac Peak Overlap", y = "Detected Targets")
```

### Promoters Only

```{r glm-prom, fig.height=7, fig.cap = "Family-wise 95% Confidence Intervals for the probability of overlapping an H3K27ac-derived promoter, based on the combinations of detected ChIP targets."}
grp_prom <- dht_consensus %>% 
  as_tibble() %>% 
  dplyr::select(range, all_of(targets), promoter) %>% 
  pivot_longer(cols = all_of(targets), names_to = "targets") %>% 
  dplyr::filter(value) %>% 
  group_by(range, promoter) %>% 
  summarise(targets = paste(targets, collapse = "+"), .groups = "drop")
glm_prom <- glm(promoter ~ 0 + targets, family = "binomial", data = grp_prom)
glm_prom %>% 
  glht() %>% 
  confint() %>% 
  .[["confint"]] %>% 
  as_tibble(rownames = "targets") %>% 
  mutate(
    n_targets = str_count(targets, "\\+") + 1
  ) %>% 
  arrange(desc(n_targets), desc(targets)) %>% 
  mutate(
    targets = fct_inorder(targets) %>% 
      fct_relabel(str_remove_all, pattern = "targets"),
    p = inv.logit(Estimate),
    TFAP2B = ifelse(str_detect(targets, "TFAP2B"), "TFAP2B", "No TFAP2B"),
    across(all_of(c("upr", "lwr")), inv.logit)
  ) %>% 
  ggplot(aes(p, targets)) + 
  geom_point() +
  geom_errorbarh(aes(xmin = lwr, xmax = upr), height = 0.4, colour = "grey20") +
  facet_grid(TFAP2B ~ ., scales = "free_y") +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x = "Probability of Promoter Overlap", y = "Detected Targets")
```


### Enhancers Only

```{r glm-enh, fig.height=7, fig.cap = "Family-wise 95% Confidence Intervals for the probability of overlapping an H3K27ac-derived enhancer, based on the combinations of detected ChIP targets."}
grp_enh <- dht_consensus %>% 
  as_tibble() %>% 
  dplyr::select(range, all_of(targets), enhancer) %>% 
  pivot_longer(cols = all_of(targets), names_to = "targets") %>% 
  dplyr::filter(value) %>% 
  group_by(range, enhancer) %>% 
  summarise(targets = paste(targets, collapse = "+"), .groups = "drop")
glm_enh <- glm(enhancer ~ 0 + targets, family = "binomial", data = grp_enh)
glm_enh %>% 
  glht() %>% 
  confint() %>% 
  .[["confint"]] %>% 
  as_tibble(rownames = "targets") %>% 
  mutate(
    n_targets = str_count(targets, "\\+") + 1
  ) %>% 
  arrange(desc(n_targets), desc(targets)) %>% 
  mutate(
    targets = fct_inorder(targets) %>% 
      fct_relabel(str_remove_all, pattern = "targets"),
    p = inv.logit(Estimate),
    TFAP2B = ifelse(str_detect(targets, "TFAP2B"), "TFAP2B", "No TFAP2B"),
    across(all_of(c("upr", "lwr")), inv.logit)
  ) %>% 
  ggplot(aes(p, targets)) + 
  geom_point() +
  geom_errorbarh(aes(xmin = lwr, xmax = upr), height = 0.4, colour = "grey20") +
  facet_grid(TFAP2B ~ ., scales = "free_y") +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x = "Probability of Enhancer Overlap", y = "Detected Targets")
```

### All Features

```{r fit-multinomial, results='hide', fig.show='asis', fig.height=6, fig.cap = "Probabilities of group membership for overlapping a promoter, enhancer, or having no H3K27ac overlap. Combinations of ChIP targets are shown based on coincident binding of TFAP2B. Intervals represent 1 - &alpha; Confidence Intervals, as described in the text. Co-binding of TFAP2&beta; was strongly associated with an increased probability of a site being associated with H3K27ac peaks as defined previously."}
df <- dht_consensus %>% 
  as_tibble() %>% 
  mutate(
    ol = case_when(
      promoter ~ "Promoter",
      enhancer ~ "Enhancer",
      TRUE ~ "No H3K27ac"
    ) %>% 
      fct_infreq()
  ) %>% 
  pivot_longer(all_of(targets), names_to = "target") %>% 
  dplyr::filter(value) %>% 
  group_by(range, ol) %>% 
  summarise(
    targets = paste(target, collapse = "+"),
    .groups = "drop"
  ) %>% 
  mutate(n_targets = 1 + str_count(targets, "\\+")) %>% 
  arrange(n_targets, targets) %>% 
  mutate(targets = fct_inorder(targets))
glm_all <- multinom(ol~ 0 + targets, data = df) 
ci_all <- Effect("targets", glm_all, confint = TRUE, confidence.level = 1 - 0.05/15)
list(
  tibble(targets = ci_all$variables$targets$levels) %>% 
    bind_cols(ci_all$prob) %>% 
    pivot_longer(starts_with("prob"), names_to = "ol") %>% 
    mutate(ol = str_remove_all(ol, "prob."), type = "p"),
  tibble(targets = ci_all$variables$targets$levels) %>% 
    bind_cols(ci_all$lower.prob) %>% 
    pivot_longer(starts_with("L.prob"), names_to = "ol") %>% 
    mutate(ol = str_remove_all(ol, "L.prob."), type = "lwr"),
  tibble(targets = ci_all$variables$targets$levels) %>% 
    bind_cols(ci_all$upper.prob) %>% 
    pivot_longer(starts_with("U.prob"), names_to = "ol") %>% 
    mutate(ol = str_remove_all(ol, "U.prob."), type = "upr")
) %>% 
  bind_rows() %>% 
  pivot_wider(names_from = "type", values_from = value) %>% 
  mutate(
    ol = str_replace_all(ol, "\\.", " ") %>% factor(levels = levels(df$ol)),
    TFAP2B = ifelse(str_detect(targets, "TFAP2B"), "TFAP2B", "No TFAP2B"),
    targets = factor(targets, levels = levels(df$targets)) %>% 
      fct_relabel(str_remove_all, pattern = "\\+TFAP2B"),
    y = case_when(
      TFAP2B == "TFAP2B" ~ as.integer(targets) + 0.2,
      TFAP2B != "TFAP2B" ~ as.integer(targets) - 0.2
    )
  ) %>% 
  # dplyr::filter(ol %in% c("Promoter", "Enhancer")) %>% 
  ggplot(aes(p, y, colour = TFAP2B)) +
  geom_point() +
  geom_errorbarh(aes(xmin = lwr, xmax = upr), height = 0.25) +
  facet_grid(.~ol, scales = "free_y", space = "free") +
  scale_y_continuous(
    breaks = str_remove_all(levels(df$targets), "\\+TFAP2B") %>% 
      unique() %>% 
      seq_along(),
    labels = str_remove_all(levels(df$targets), "\\+TFAP2B") %>% 
      unique()
  ) +
  scale_colour_manual(values = c("grey70", rgb(0.9, 0.1, 0.2))) +
  labs(
    x = expression(pi[i]),
    y = "Targets"
  )
```

A simple multinomial model was then fit using the possible outcomes (or classes) for each site: 1) Promoter Overlap; 2) Enhancer Overlap, or 3) No H3K27ac overlap.
$1 - \alpha$ confidence intervals for the probability of class membership were then estimated using $\alpha = 0.05/15$, given there were 15 combinations of transcription factors detected.

## Distance to Nearest TSS

The distance to the nearest TSS was also checked for each of the union peaks, with the vast majority of TFAP2$\beta$-only peaks being with 1kb of a TSS, indicating a fundamental role for TFAP2$\beta$ in transcriptional regulation.
These were much further away when bound in combination with other ChIP targets, to the point that most sites where all four were found bound were >3kb from any TSS, suggesting that an alternative role for TFAP2$\beta$ is enhancer-based gene regulation, when acting in concert with the remaining targets.

```{r dist-to-tss, fig.height = 10, fig.cap = "Distance to the nearest TSS for all peaks detected with one or more of the required ChIP targets."}
dht_consensus %>% 
  as_tibble() %>% 
  dplyr::select(range, all_of(targets), dist_to_tss, H3K27ac) %>% 
  pivot_longer(cols = all_of(targets), names_to = "targets") %>% 
  dplyr::filter(value) %>% 
  group_by(range, dist_to_tss, H3K27ac) %>% 
  arrange(range, targets) %>% 
  summarise(targets = paste(targets, collapse = "+"), .groups = "drop") %>% 
  mutate(
    n_targets = str_count(targets, "\\+") + 1,
    TFAP2B = ifelse(str_detect(targets, "TFAP2B"), "TFAP2B", "No TFAP2B")
  ) %>% 
  arrange(desc(n_targets), desc(targets)) %>% 
  mutate(targets = fct_inorder(targets)) %>% 
  ggplot(aes(dist_to_tss + 1, targets, fill = H3K27ac)) +
  # geom_boxplot() +
  geom_violin(draw_quantiles = 0.5) +
  facet_grid(TFAP2B ~ ., scales = "free_y") +
  scale_x_log10(labels = comma, breaks = 10^seq(0, 5)) +
  scale_fill_manual(values = c("grey70", rgb(0.9, 0.1, 0.2))) +
  labs(x = "Distance to Nearest TSS (bp+1)", y = "ChIP Targets")
```

```{r dist-to-tss-densities, eval = FALSE}
dht_consensus %>% 
  as_tibble() %>% 
  # sample_n(10000) %>% 
  dplyr::select(range, all_of(targets), dist_to_tss, H3K27ac) %>% 
  pivot_longer(cols = all_of(targets), names_to = "targets") %>% 
  dplyr::filter(value) %>% 
  group_by(range, dist_to_tss, H3K27ac) %>% 
  arrange(range, targets) %>% 
  summarise(targets = paste(targets, collapse = "+"), .groups = "drop") %>% 
  mutate(
    n_targets = str_count(targets, "\\+") + 1,
    TFAP2B = ifelse(str_detect(targets, "TFAP2B"), "TFAP2B", "No TFAP2B")
  ) %>% 
  arrange(desc(n_targets), desc(targets)) %>% 
  mutate(
    targets = str_remove_all(targets, "\\+TFAP2B"),
    targets = fct_inorder(targets)
  ) %>% 
  ggplot(aes(dist_to_tss + 1, stat(density), colour = TFAP2B, linetype = H3K27ac)) +
  geom_density() +
  facet_wrap(.~targets) +
  scale_colour_manual(values = c("grey70", rgb(0.9, 0.1, 0.2))) +
  scale_linetype_manual(values = c(2, 1)) +
  scale_x_log10(labels = comma, breaks = 10^c(0:5))
```


### Comparison With H3K27ac HiChIP Data


```{r hic}
fl <- here::here("data", "hichip") %>% 
  list.files(full.names = TRUE, pattern = "gi.+rds") 
hic <- GInteractions()
for (f in fl) {
  hic <- c(hic, read_rds(f))
}
hic <- sort(hic)
```

H3K27ac-HiChIP obtained from [SRA](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE157381) and [analysed previously](https://github.com/DRMCRL/MDA-MB-453-H3K27Ac-HiChIP), was additionally included to improve mapping of peaks to genes.
Whilst the previous H3K27ac-derived features were obtained from the same passages/experiments as GATA3 and AR, HiChIP data was obtained from a public dataset, not produced with the DRMCRL, and were defined using only the Vehicle controls from an Abemaciclib Vs. Vehicle experiment.
Long range interactions were included for bin sizes of `r pander(sort(as.numeric(unique(hic$bin_size)))/1e3)` kb.
Before proceeding, the comparability of the H3K27ac-HiChIP and H3K27ac-derived features was checked.
`r percent(length(subsetByOverlaps(hic, features)) / length(hic))` of HiChIP long-range interactions overlapped a promoter or enhancer derived from H3K27ac ChIP-seq.
Conversely, `r percent(length(subsetByOverlaps(features, hic)) / length(features))` or ChIP-Seq features mapped to a long-range interaction, confirming that the H3K27ac signatures within MDA-MB-453 cells are highly comparable across laboratories.

## Comparison To Key Genes

```{r plot-setup}
data("grch37.cytobands")
tm <- read_rds(
  here::here("data", "annotations", "trans_models.rds")
)
bwfl <- list(
  AR = here::here("data", "bigwig", "AR") %>% 
    list.files(pattern = "DHT_merged.+bw", full.names = TRUE) %>% 
    BigWigFileList() %>% 
    setNames(
      path(.) %>% 
        basename() %>% 
        str_remove_all("_merged_treat.+")
    ),
  FOXA1 = here::here("data", "bigwig", "FOXA1") %>% 
    list.files(pattern = "DHT_merged.+bw", full.names = TRUE) %>% 
    BigWigFileList() %>% 
    setNames(
      path(.) %>% 
        basename() %>% 
        str_remove_all("_merged_treat.+")
    ),
  GATA3 = here::here("data", "bigwig", "GATA3") %>% 
    list.files(pattern = "DHT_merged.+bw", full.names = TRUE) %>% 
    BigWigFileList() %>% 
    setNames(
      path(.) %>% 
        basename() %>% 
        str_remove_all("_merged_treat.+")
    ),
  TFAP2B = here::here("data", "bigwig", "TFAP2B") %>% 
    list.files(pattern = "DHT_merged.+bw", full.names = TRUE) %>% 
    BigWigFileList() %>% 
    setNames(
      path(.) %>% 
        basename() %>% 
        str_remove_all("_merged_treat.+")
    ),
  H3K27ac = here::here("data", "bigwig", "H3K27ac") %>% 
    list.files(pattern = "merged_DHT.bw", full.names = TRUE) %>% 
    BigWigFileList() %>% 
    setNames(
      path(.) %>% 
        basename() %>% 
        str_extract("DHT|Veh")
    )
) %>% 
  lapply(path) %>% 
  lapply(as.character) %>% 
  BigWigFileList()
y_lim <- here::here("data", "bigwig", targets) %>% 
  sapply(
    list.files, pattern = "merged.*summary", full.names= TRUE, simplify = FALSE
  ) %>% 
  lapply(
    function(x) lapply(x, read_tsv)
  ) %>% 
  lapply(bind_rows) %>% 
  lapply(function(x) c(0, max(x$score))) %>% 
  setNames(basename(names(.)))
y_lim$H3K27ac <- bwfl$H3K27ac %>% 
  import.bw %>% 
  mcols() %>% 
  .[["score"]] %>% 
  max() %>% 
  c(0) %>% 
  range()
```


## Mapping To Detected Genes {.tabs}


```{r all-gr}
rnaseq <- here::here("data", "rnaseq", "dge.rds") %>% 
  read_rds()
counts <- here::here("data", "rnaseq", "counts.out.gz") %>% 
  read_tsv(skip = 1) %>% 
  dplyr::select(Geneid, ends_with("bam")) 
detected <- counts %>%
  pivot_longer(
    cols = ends_with("bam"), names_to = "sample", values_to = "counts"
  ) %>% 
  mutate(detected = counts > 0) %>% 
  group_by(Geneid) %>% 
  summarise(detected = mean(detected) > 0.25, .groups = "drop") %>%
  dplyr::filter(detected) %>% 
  pull("Geneid")
top_table <- here::here("data", "rnaseq", "MDA-MB-453_RNASeq.tsv") %>% 
  read_tsv() # Not a DHT-treatment analysis though...
```

```{r map-to-genes}
dht_consensus <- mapByFeature(
  dht_consensus, 
  genes = subset(all_gr$gene, gene_id %in% detected),
  prom = subset(features, feature == "promoter"),
  ## Given we have accuracte H3K27ac HiChIP, better mappings can be gained that way.
  ## Exclude any enhancers which overlap the HiChIP
  enh = subset(features, feature == "enhancer") %>% filter_by_non_overlaps(hic),
  gi = hic
) %>% 
  mutate(mapped = vapply(gene_id, function(x) length(x) > 0, logical(1)))
all_targets <- dht_consensus %>% 
  as_tibble() %>% 
  dplyr::filter(if_all(all_of(targets))) %>% 
  unnest(everything()) %>% 
  distinct(gene_id) %>% 
  pull("gene_id")
```

In order to more accurately assign genes to actively transcribed genes, the RNA-Seq dataset generated in 2013 studying DHT Vs. Vehicle in MDA-MB-453 cells was used to define the set of genes able to be considered as detected.
As this was a polyA dataset, some ncRNA which are not adenylated may be expressed, but will remain as undetected despite this technological limitation.
All `r comma(length(detected))` genes with >1 read in at least 1/4 of the samples was considered to be detected, and peaks were only mapped to detected genes.

Mapping was performed using `mapByFeature()` from the package `extraChIP` using:

1. Promoters defined externally using H3K27ac
2. Only the externally defined enhancers which contained no H3K27ac-HiChIP overlap
3. H3K27ac HiChIP interactions for long range mapping

No separate enhancers were using in the mapping steps as the H3K27ac-HiChIP interaction were considered to provide clear associations between peaks and target genes.
By contrast, the default mapping of `mapByFeature()` would map all genes within 100kb to any peak considered as an enhancer


`r dht_consensus %>% as_tibble() %>% unnest(everything()) %>% distinct(gene_id) %>% nrow() %>%  divide_by(length(detected)) %>% percent()` of detected genes had one or more peaks mapped to them.

Looking specifically at the peaks for which all four targets directly overlapped, `r comma(length(all_targets))` of the `r comma(length(detected))` detected genes were mapped to at least one directly overlapping binding region.


## Apocrine Signature Enrichment

### Subtype Gene Signatures

```{r load-apo}
hgnc <- read_csv(
  here::here("data", "external", "hgnc-symbol-check.csv"), skip = 1
) %>% 
  dplyr::select(Gene = Input, gene_name = `Approved symbol`)
apo_ranks <- here::here("data", "external", "ApoGenes.txt") %>% 
  read_tsv() %>% 
  left_join(hgnc) %>% 
  left_join(
    as_tibble(all_gr$gene) %>% 
      dplyr::select(gene_id, gene_name),
    by = "gene_name"
  ) %>% 
  dplyr::select(starts_with("gene_"), ends_with("rank")) %>% 
  dplyr::filter(!is.na(gene_id))
apo_full <- read_excel(
  here::here("data", "external", "Apocrine gene lists.xls"),
  col_names = c(
    "Gene", 
    paste0("ESR1", c("_logFC", "_p")),
    paste0("CLCA2", c("_logFC", "_p")),
    paste0("DCN", c("_logFC", "_p")),
    paste0("GZMA", c("_logFC", "_p")),
    paste0("MX1", c("_logFC", "_p")),
    paste0("TPX2", c("_logFC", "_p")),
    paste0("FABP4", c("_logFC", "_p")),
    paste0("ADM", c("_logFC", "_p")),
    paste0("CD83", c("_logFC", "_p"))
    ),
  col_types = c("text", rep("numeric", 18)),
  skip = 1
) %>% 
  left_join(hgnc) %>% 
  left_join(
    as_tibble(all_gr$gene) %>% 
      dplyr::select(gene_id, gene_name),
    by = "gene_name"
  ) %>% 
  dplyr::select(starts_with("gene", FALSE), matches("_(logFC|p)"))
apo_genesets <- colnames(apo_full) %>% 
  str_subset("_p$") %>% 
  sapply(
    function(x) {
      dplyr::filter(apo_full, !!sym(x) < 0.05, !is.na(gene_name))$gene_name
    },
    simplify = FALSE
  ) %>% 
  setNames(
    str_remove(names(.), pattern = "_p")
  )
genes_by_subtype <- apo_genesets %>% 
  lapply(list) %>% 
  as_tibble() %>% 
  pivot_longer(everything(), names_to = "subtype", values_to = "gene_name") %>% 
  unnest(everything()) %>% 
  split(.$gene_name) %>% 
  lapply(pull, "subtype")
```


The models for different subtypes, as [previously published](https://www.nature.com/articles/1208561) were loaded, with a signature from each subtype being derived from genes with an adjusted p-value < 0.05, as initially published.
This gave `r length(apo_genesets)` different gene-sets with key marker genes denoting the subtypes: `r pander(names(apo_genesets))`

```{r upset-signatures, fig.height=7, fig.cap = "UpSet plot showing the association between genes contained in each signature. A relatively high degree of similarity was noted between some signature pairs, such as GZMA/CD83 and MX1/GZMA"}
apo_genesets %>% 
  fromList() %>% 
  upset(
    sets = rev(names(.)), 
    # keep.order = TRUE,
    order.by = "freq",
    set_size.show = TRUE,
    set_size.scale_max = nrow(.) * 0.4
  )
```


```{r corrplot-signatures, fig.height=6, fig.width=6, fig.cap = "Correlation plot between signatures based on shared genes between groups"}
apo_genesets %>% 
  fromList() %>%
  cor() %>% 
  corrplot(
    diag = FALSE, 
    addCoef.col = "grey50",
    addCoefasPercent = TRUE
  )
```


### Enrichment Testing {.tabset}

The set of genes mapped to sites contain all four ChIP targets were then tested for enrichment of any of the defined signatures.
Enrichment testing as implemented in `goseq` was used, incorporating the number of consensus peaks mapped to a gene as the offset term for biased sampling.

#### All Common Sites

```{r pwf-all4, fig.width=8, fig.height=6, fig.cap = "PWF for biased sampling using the number of peaks mapped to a gene as the bias offset"}
mapped <- all_gr$gene %>% 
  filter(gene_id %in% detected) %>% 
  mutate(gene_width = width) %>% 
  as_tibble() %>% 
  dplyr::select(starts_with("gene")) %>% 
  mutate(
    mapped_to_all = gene_name %in% unlist(filter(dht_consensus, !!!syms(targets))$gene_name),
    n_peaks = table(unlist(dht_consensus$gene_name))[gene_name] %>% 
      as.integer(),
    n_peaks = ifelse(is.na(n_peaks), 0, n_peaks)
  ) %>% 
  distinct(gene_name, .keep_all = TRUE)
goseq_all4 <- structure(
  mapped$mapped_to_all, names = mapped$gene_name
) %>% 
  nullp(bias.data = mapped$n_peaks) %>%  
  goseq(gene2cat = genes_by_subtype) %>% 
  as_tibble() %>% 
  dplyr::select(
    subtype = category,
    p = over_represented_pvalue,
    n_mapped = numDEInCat,
    signature_size = numInCat
  ) %>% 
  mutate(fdr = p.adjust(p, "fdr"))
```

```{r res-goseq-all4}
goseq_all4 %>% 
  mutate(`%` = percent(n_mapped / signature_size, accuracy = 0.1)) %>% 
  dplyr::select(
    Subtype = subtype, `Signature Size` = signature_size, `# Mapped` = n_mapped,
    `% Mapped` = `%`, p, FDR = fdr
  ) %>% 
  pander(
    justify = "lrrrrr",
    caption = paste(
      "Results for Subtype enrichment testing using all genes mapped to any ",
      "consensus peak, where all four ChIP targets were considered to be present."
    ),
    emphasize.strong.rows = which(.$FDR < 0.05)
  )
```

#### H3K27Ac-Associated Common Sites

The same process was then performed restricting the mappings to those sites associated with H3K27ac binding.

```{r pwf-h3k, fig.width=8, fig.height=6, fig.cap = "PWF for biased sampling using the number of peaks mapped to a gene as the bias offset"}
mapped_h3k <- all_gr$gene %>% 
  filter(gene_id %in% detected) %>% 
  mutate(gene_width = width) %>% 
  as_tibble() %>% 
  dplyr::select(starts_with("gene")) %>% 
  mutate(
    mapped_to_all = gene_name %in% unlist(filter(dht_consensus, !!!syms(targets), H3K27ac)$gene_name),
    n_peaks = table(unlist(dht_consensus$gene_name))[gene_name] %>% 
      as.integer(),
    n_peaks = ifelse(is.na(n_peaks), 0, n_peaks)
  ) %>% 
  distinct(gene_name, .keep_all = TRUE)
goseq_h3k <- structure(
  mapped_h3k$mapped_to_all, names = mapped_h3k$gene_name
) %>% 
  nullp(bias.data = mapped_h3k$n_peaks) %>%  
  goseq(gene2cat = genes_by_subtype) %>% 
  as_tibble() %>% 
  dplyr::select(
    subtype = category,
    p = over_represented_pvalue,
    n_mapped = numDEInCat,
    signature_size = numInCat
  ) %>% 
  mutate(fdr = p.adjust(p, "fdr"))
```

```{r res-goseq-h3k}
goseq_h3k %>% 
  mutate(`%` = percent(n_mapped / signature_size, accuracy = 0.1)) %>% 
  dplyr::select(
    Subtype = subtype, `Signature Size` = signature_size, `# Mapped` = n_mapped,
    `% Mapped` = `%`, p, FDR = fdr
  ) %>% 
  pander(
    justify = "lrrrrr",
    caption = paste(
      "Results for Subtype enrichment testing using only genes mapped to a",
      "consensus peak *associated with H3K27ac activity*, and where all four", 
      "ChIP targets were considered to be present."
    ),
    emphasize.strong.rows = which(.$FDR < 0.05)
  )
```

#### H3K27ac Associated Sites Without TFAP2B

The same process was then performed restricting the mappings to those sites associated with H3K27ac binding, where AR, FOXA1 and GATA3 are all bound but without TFAP2B.

```{r pwf-noap2b, fig.width=8, fig.height=6, fig.cap = "PWF for biased sampling using the number of peaks mapped to a gene as the bias offset"}
mapped_noap2b <- all_gr$gene %>% 
  filter(gene_id %in% detected) %>% 
  mutate(gene_width = width) %>% 
  as_tibble() %>% 
  dplyr::select(starts_with("gene")) %>% 
  mutate(
    mapped_to_all = gene_name %in% unlist(filter(dht_consensus, AR, FOXA1, GATA3, !TFAP2B, H3K27ac)$gene_name),
    n_peaks = table(unlist(dht_consensus$gene_name))[gene_name] %>% 
      as.integer(),
    n_peaks = ifelse(is.na(n_peaks), 0, n_peaks)
  ) %>% 
  distinct(gene_name, .keep_all = TRUE)
goseq_noap2b <- structure(
  mapped_noap2b$mapped_to_all, names = mapped_noap2b$gene_name
) %>% 
  nullp(bias.data = mapped_noap2b$n_peaks) %>%  
  goseq(gene2cat = genes_by_subtype) %>% 
  as_tibble() %>% 
  dplyr::select(
    subtype = category,
    p = over_represented_pvalue,
    n_mapped = numDEInCat,
    signature_size = numInCat
  ) %>% 
  mutate(fdr = p.adjust(p, "fdr"))
```

```{r res-goseq-noap2b}
goseq_noap2b %>% 
  mutate(`%` = percent(n_mapped / signature_size, accuracy = 0.1)) %>% 
  dplyr::select(
    Subtype = subtype, `Signature Size` = signature_size, `# Mapped` = n_mapped,
    `% Mapped` = `%`, p, FDR = fdr
  ) %>% 
  pander(
    justify = "lrrrrr",
    caption = paste(
      "Results for Subtype enrichment testing using only genes mapped to a",
      "consensus peak *associated with H3K27ac activity*, and where AR, FOXA1", 
      "and GATA3 were considered to be present, but in the absence of TFAP2B."
    ),
    emphasize.strong.rows = which(.$FDR < 0.05)
  )
```

#### H3K27ac Associated Sites Without AR

The same process was then performed restricting the mappings to those sites associated with H3K27ac binding, where FOXA1, GATA3 and TFAP2B are all bound but without taking AR binding into account.

```{r pwf-noar, fig.width=8, fig.height=6, fig.cap = "PWF for biased sampling using the number of peaks mapped to a gene as the bias offset"}
mapped_noar <- all_gr$gene %>% 
  filter(gene_id %in% detected) %>% 
  mutate(gene_width = width) %>% 
  as_tibble() %>% 
  dplyr::select(starts_with("gene")) %>% 
  mutate(
    mapped_to_all = gene_name %in% unlist(filter(dht_consensus, FOXA1, GATA3, TFAP2B, H3K27ac)$gene_name),
    n_peaks = table(unlist(dht_consensus$gene_name))[gene_name] %>% 
      as.integer(),
    n_peaks = ifelse(is.na(n_peaks), 0, n_peaks)
  ) %>% 
  distinct(gene_name, .keep_all = TRUE)
goseq_noar <- structure(
  mapped_noar$mapped_to_all, names = mapped_noar$gene_name
) %>% 
  nullp(bias.data = mapped_noar$n_peaks) %>%  
  goseq(gene2cat = genes_by_subtype) %>% 
  as_tibble() %>% 
  dplyr::select(
    subtype = category,
    p = over_represented_pvalue,
    n_mapped = numDEInCat,
    signature_size = numInCat
  ) %>% 
  mutate(fdr = p.adjust(p, "fdr"))
```

```{r res-goseq-noar}
goseq_noar %>% 
  mutate(`%` = percent(n_mapped / signature_size, accuracy = 0.1)) %>% 
  dplyr::select(
    Subtype = subtype, `Signature Size` = signature_size, `# Mapped` = n_mapped,
    `% Mapped` = `%`, p, FDR = fdr
  ) %>% 
  pander(
    justify = "lrrrrr",
    caption = paste(
      "Results for Subtype enrichment testing using only genes mapped to a",
      "consensus peak *associated with H3K27ac activity*, and where FOXA1", 
      "GATA3 and TFAP2B were considered to be present, but in the absence of AR."
    ),
    emphasize.strong.rows = which(.$FDR < 0.05)
  )
```


### Sequence Export

```{r seq-export}
hg19 <- BSgenome.Hsapiens.UCSC.hg19
sq19 <- seqinfo(hg19)
consenus_hg19 <- dht_consensus
seqinfo(consenus_hg19) <- sq19
features_hg19 <- features
seqinfo(features_hg19) <- sq19

getSeq(
  hg19,
  consenus_hg19 %>% 
    filter(AR, FOXA1, GATA3, !TFAP2B) %>% 
    resize(width = 500, fix = 'center') %>% 
    setNames(as.character(.))
) %>% 
  writeXStringSet(
    here::here("output", "ar_foxa1_gata3_no_tfap2b.fa")
  )
getSeq(
  hg19,
  consenus_hg19 %>% 
    filter(AR, FOXA1, GATA3, TFAP2B) %>% 
    resize(width = 500, fix = 'center') %>% 
    setNames(as.character(.))
) %>% 
  writeXStringSet(
    here::here("output", "ar_foxa1_gata3_tfap2b.fa")
  )
getSeq(
  hg19,
  consenus_hg19 %>% 
    filter(AR, FOXA1, GATA3, TFAP2B, H3K27ac) %>% 
    resize(width = 500, fix = 'center') %>% 
    setNames(as.character(.))
) %>% 
  writeXStringSet(
    here::here("output", "all4_h3k27ac.fa")
  )
getSeq(
  hg19,
  consenus_hg19 %>% 
    filter(AR, FOXA1, GATA3, TFAP2B, !H3K27ac) %>% 
    resize(width = 500, fix = 'center') %>% 
    setNames(as.character(.))
) %>% 
  writeXStringSet(
    here::here("output", "all4_no_h3k27ac.fa")
  )
```



## Visualisations: Luminal Genes {.tabset}

### MYC

As the gene *MYC* has been identified as a key target, the binding patterns within the gene were explored.
The two binding sites 1) with all four ChIP targets detected, 2) within 100kb of *MYC*, and 3) which were connected using HiChIP interactions were visualised and exported.

```{r plot-myc, fig.height=10, fig.width=10, results='hide', fig.cap = "Two joint binding sites either side of *MYC* connected by HiChIP interactions to the promoter. HiChIP connections were detected at all bin sizes, however, only fine-resolutions 5kb interaction bins are shown."}
gn <- "MYC"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  arrange(d) %>% 
  filter(d < 1e5)
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) <= 5e3),
  hicsize = 3,
  max = 5e7,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 3*width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### GATA3

```{r plot-gata3, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, and which map to *GATA3*. Only the high-resolution 5kb bins are shown."}
gn <- "GATA3"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  arrange(d) %>% 
  subsetByOverlaps(
    hic %>% 
      subset(as.integer(bin_size) == 5e3) %>% 
      subsetByOverlaps(
        subset(all_gr$gene, gene_name == gn)
      )
  )
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) <= 5e3),
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
region_plot$Detected@dp@pars$just.group <- "right"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 3*width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### FOXA1

```{r plot-foxa1,  fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, and which map to *FOXA1*. Only the high-resolution 5kb bins are shown."}
gn <- "FOXA1"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  arrange(d) %>%
  subsetByOverlaps(
    hic %>%
      subset(as.integer(bin_size) == 5e3) %>%
      subsetByOverlaps(
        subset(all_gr$gene, gene_name == gn)
      )
  )
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) <= 5e3),
  max = 1e5,
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.2,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 1.5 * width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### XBP1

```{r plot-xbp1, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, and which are within 100kb of *XBP1*. Only the high-resolution 5kb interaction bins are shown. The two additional peaks were not considered to show evidence of TFAP2B binding by macs2 callpeak and are not highlighted for this reason"}
gn <- "XBP1"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  arrange(d) %>% 
  filter(d < 100e3)
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) == 5e3),
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 1.5 * width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### MYB

```{r plot-myb, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, and which map to *MYB*. Only the low-resolution 20kb interaction bins are shown."}
gn <- "MYB"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  arrange(d) 
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) == 20e3),
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 1.5 * width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### GREB1

```{r plot-greb1, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, and which map to *GREB1*. Only the low-resolution 40kb interaction bins are shown."}
gn <- "GREB1"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  arrange(d) 
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) <= 40e3),
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 5 * width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### AR

```{r plot-ar, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, which map to *AR* and are within 100kb of the gene. Only the low-resolution 20kb HiC interaction bins are shown."}
gn <- "AR"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  filter(d < 1e5)
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>%
    subset(as.integer(bin_size) == 20e3),
  hicsize = 3,
  max = 5e4,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 6,
  shift = -6e4,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 3 * width(gr), fix = 'center') %>% 
    range()
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```



## Visualisations:: Apocrine Genes {.tabset}

### CLCA2

```{r plot-clca2, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, and which within the transcribed region for *CLCA2*. No HiC data is shown."}
gn <- "CLCA2"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  arrange(d) 
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  collapseTranscripts = "meta",
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 4,
  shift = 1e4,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 1.2 * width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### TFAP2B

```{r plot-tfap2b, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, which map to *TFAP2B* and are within 500kb of *TFAP2B*. Only the medium-resolution 10kb interaction bins are shown."}
gn <- "TFAP2B"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  filter(d < 5e5) 
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) == 10e3),
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 3 * width(gr), fix = 'center') %>% 
    reduce()
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### KYNU

```{r plot-kynu, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, and which map to *KYNU*. No HiC interaction bins were found in this region."}
gn <- "KYNU"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) 
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) <= 40e3),
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 5,
  shift = 3e4,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 1.5 * width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.1*width(.), fix = 'center') %>% 
  resize(width = 0.4 * width(.), fix = 'start')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### DUSP6

```{r plot-dusp6, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, which map to *DUSP6* and are within 100kb of the gene. Only the high-resolution 5kb HiC interaction bins are shown."}
gn <- "DUSP6"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  filter(d < 1e5)
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) <= 5e3),
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  shift = 3e4,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 3 * width(gr), fix = 'center') %>% 
    reduce()
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 0.8 * width(.), fix = 'center') %>% 
  shift(1e4)
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

### FGFR4

```{r plot-fgfr4, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, which map to *FGFR4* and are within 100kb of the gene. Only the high-resolution 5kb HiC interaction bins are shown."}
gn <- "FGFR4"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  filter(d < 1e5)
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) <= 5e3),
  hicsize = 3,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 2 * width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```


### PGAP3

```{r plot-pgap3, fig.height=10, fig.width=10, results='hide', fig.cap = "All H3K27ac-associated peaks where all four targets were detected, which map to *PGAP3* and are within 100kb of the gene. Only the high-resolution 5kb HiC interaction bins are shown."}
gn <- "PGAP3"
gr <- dht_consensus %>% 
  filter(!!!syms(targets), mapped, H3K27ac) %>% 
  filter(
    vapply(gene_name, function(x) gn %in% x, logical(1))
  ) %>% 
  mutate(d = distance(., subset(all_gr$gene, gene_name == gn))) %>% 
  filter(d < 1e5)
fs <- 14
region_plot <- plotHFGC(
  gr = gr,
  hic = hic %>%
    subsetByOverlaps(gr) %>%
    subsetByOverlaps(
      subset(all_gr$gene, gene_name == gn)
    ) %>% 
    subset(as.integer(bin_size) <= 5e3),
  hicsize = 3,
  max = 5e4,
  genes = tm %>%
    mutate(detected = ifelse(gene %in% detected, "Detected", "Not-Detected")) %>%
    split(.$detected),
  genecol = c(
    Detected = "forestgreen", "Not-Detected" = rgb(0.2, 0.2, 0.7, 0.5)
  ),
  coverage = bwfl, 
  linecol = rep("grey30", length(bwfl)),
  cytobands = grch37.cytobands,
  zoom = 1.1,
  highlight = rgb(0, 0, 1, 0.5), 
  title.width = 1, 
  col.title = "black", background.title = "white",
  showAxis = FALSE,
  rotation.title = 90, fontsize = fs, 
  fontface.title = 1,
  legend = FALSE,
  fontcolor.legend = "black"
)
region_plot[[1]]@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$fontcolor <- "black"
region_plot$Axis@dp@pars$col <- "grey30"
if ("HiC" %in% names(region_plot)) {
  region_plot$HiC@name <- "HiChIP"
  region_plot$HiC@dp@pars$fontface.title <- 1
  region_plot$HiC@dp@pars$rotation.title <- 0
}
region_plot$Detected@dp@pars$fontface.title <- 1
region_plot$Detected@dp@pars$rotation.title <- 0
region_plot$Detected@dp@pars$fontsize.group <- fs
region_plot$Detected@dp@pars$cex.group <- 0.8
region_plot$Detected@dp@pars$fontface.group <- 1
region_plot$Detected@dp@pars$fontcolor.group <- "black"
if ("Not-Detected" %in% names(region_plot)) {
  region_plot$`Not-Detected`@dp@pars$fontcolor.group <- "black"
  region_plot$`Not-Detected`@dp@pars$fontface.title <- 1
  region_plot$`Not-Detected`@dp@pars$rotation.title <- 0
  region_plot$`Not-Detected`@dp@pars$fontsize.group <- fs
  region_plot$`Not-Detected`@dp@pars$cex.group <- 0.8
  region_plot$`Not-Detected`@dp@pars$fontface.group <- 1
  region_plot$`Not-Detected`@dp@pars$just.group <- "right"
}
region_plot$AR@dp@pars$rotation.title <- 0
region_plot$FOXA1@dp@pars$rotation.title <- 0
region_plot$GATA3@dp@pars$rotation.title <- 0
region_plot$TFAP2B@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$rotation.title <- 0
region_plot$H3K27ac@dp@pars$size <- 5
ax <- region_plot[1:2]
top_panels <- region_plot[names(region_plot) %in% c("HiC", "Detected", "Not-Detected")]
hl <- HighlightTrack(
  region_plot[c(targets, "H3K27ac")],
  range = resize(gr, width = 1.5 * width(gr), fix = 'center')
)
hl@dp@pars$fill <- rgb(1, 1, 1, 0)
hl@dp@pars$col <- "blue"
hl@dp@pars$lwd <- 0.8
pdf(here::here("output", glue("{gn}.pdf")), width = 10, height = 10)
plot_range <- c(gr, subset(all_gr$gene, gene_name == gn)) %>% 
  range(ignore.strand = TRUE) %>% 
  resize(width = 1.2*width(.), fix = 'center')
Gviz::plotTracks(
  c(ax, top_panels, hl),
  from = start(plot_range), to = end(plot_range),
  title.width = 1,
  margin = 40,
  fontface.main = 1
  )
dev.off()
```

